\Title

### 2021-06-07 latex/paper/main.tex
First full editing pass of the paper

\subsection{Energy Gain on \(\mathcal{O}_2(\rho)\)}
Since \(\mathcal{O}_2(\rho) = \bar{\mathcal{O}}_1 \cup \mathcal{R}(\rho)\)
(where \(\mathcal{R}(\rho)\) is the rotation domain defined in
\eqref{eqn:rotation-domain}), and since all orbits escape 
\(\bar{\mathcal{O}_1}\) in finite time, we need simply prove energy gain on
\(\mathcal{R}(\rho)\) to complete the proof of Theorem
\ref{thm:acrobot-energy-stabilization}.
We separate \(\mathcal{R}(\rho)\) into its two distinct connected components:
\(\mathcal{R}^+(\rho)\), the set of rotations with \(p_u > 0\); 
and \(\mathcal{R}^-(\rho)\), the set of rotations with \(p_u < 0\).
We take the domain of interest for Lemma \ref{lemma:energy-regulation-D} to be
\(D \in \{\mathcal{R}^+(\rho), \mathcal{R}^-(\rho)\}\).

We now apply the method described in
\cite{dynamic_vhcs_stabilize_closed_orbits} to find pseudo-polar coordinates
adapted to rotations.
These coordinates are 
\begin{align}
    \label{eqn:r-rot}
    r &= \sqrt{p_u^2 - 30m^2gl^3(1-c_u)}
    , \\
    \label{eqn:theta-rot}
    \theta &= \pm q_u
\end{align}
where \(r \in \, ]\sqrt{60m^2gl^3}, \rho[\) and \(\pm\) denotes
whether \(D=\mathcal{R}^+(\rho)\) or \(D=\mathcal{R}^-(\rho)\).
The inverse of this transformation is
\begin{align*}
    q_u &= \pm \theta
    , \\
    p_u &= \pm \sqrt{r^2+30m^2gl^3(1-c_\theta)}
    .
\end{align*}

When we compute the constrained dynamics in
\((r,\theta)\) coordinates and set \(I = 0\), MATLAB symbolic computations
reveal that \(\dot{r} = 0\) and
\[
\dot{\theta} = \frac{1}{5ml^2} \sqrt{r^2 - 30m^2gl^3(1-c_\theta)}
.
\]
We thus have \(\dot{\theta} > 0\) when \(I = 0\) as required.
Defining \(g(\theta,r,I) = \dot{r}/\dot{\theta}\), MATLAB symbolic computations
also confirm that \((\partial g/\partial r)(\theta,r,0) \equiv 0\).
The function \(b(\theta,r_0) = (\partial g/\partial I)(\theta,r_0,0)\) is given
in the statement of Theorem \ref{thm:acrobot-energy-stabilization}, and by
assumption we have \(S(r_0) \geq \epsilon\) on
\(]\sqrt{60m^2gl^3},\rho[\).
Thus, all requirements of Lemma \ref{lemma:energy-regulation-D} are satisfied,
so there exists a common \(I_2(\rho)\) whereby the acrobot gains/loses
energy on both \(\mathcal{R}^+\) and \(\mathcal{R}^-\).

Let \(I_1^\star\) be the parameter we found for \(\mathcal{O}_1\) in 
Section \ref{sec:proof-o1}.
Taking \(I^{\star\star} = \min \{I_1^\star, I_2(\rho)\}\),
the acrobot gains/loses energy on \(\mathcal{O}_2(\rho)\)
when \(|I| \leq I^{\star\star}\).
This completes the proof of Theorem \ref{thm:acrobot-energy-stabilization}.

>>>>

\subsection{Energy Gain on \(\mathcal{O}_2(\rho)\)}
Since \(\mathcal{O}_2(\rho) = \bar{\mathcal{O}}_1 \cup \mathcal{R}(\rho)\)
(where \(\mathcal{R}(\rho)\) is the rotation domain defined in
\eqref{eqn:rotation-domain}), and since all orbits escape 
\(\bar{\mathcal{O}_1}\) in finite time, we need simply prove energy gain on
\(\mathcal{R}(\rho)\) to prove energy gain on \(\mathcal{O}_2(\rho)\).
We separate \(\mathcal{R}(\rho)\) into its two distinct connected components:
\(\mathcal{R}^+(\rho)\), the set of rotations with \(p_u > 0\); 
and \(\mathcal{R}^-(\rho)\), the set of rotations with \(p_u < 0\).
We take the domain of interest for Lemma \ref{lemma:energy-regulation-D} to be
\(D \in \{\mathcal{R}^+(\rho), \mathcal{R}^-(\rho)\}\).

We now apply the method described in
\cite{dynamic_vhcs_stabilize_closed_orbits} to find pseudo-polar coordinates
adapted to rotations.
These coordinates are 
\begin{align}
    \label{eqn:r-rot}
    r &= \sqrt{p_u^2 + 30m^2gl^3(1-c_u)}
    , \\
    \label{eqn:theta-rot}
    \theta &= \pm q_u
\end{align}
where \((r,\theta) \in \, ]\sqrt{60m^2gl^3}, \rho[ \times \Sone\).
The inverse of this transformation is
\begin{align*}
    q_u &= \pm \theta
    , \\
    p_u &= \pm \sqrt{r^2-30m^2gl^3(1-c_\theta)}
    .
\end{align*}
In this context, \(\pm\) denotes whether \(D=\mathcal{R}^+(\rho)\) or
\(D=\mathcal{R}^-(\rho)\).

In computing the constrained dynamics in
\((r,\theta)\) coordinates and setting \(I = 0\), 
we find that \(\dot{r} \equiv 0\) and
\[
\dot{\theta} = \frac{1}{5ml^2} \sqrt{r^2 - 30m^2gl^3(1-c_\theta)}
,
\]
which is strictly positive as required.
Defining \(g(\theta,r,I) = \dot{r}/\dot{\theta}\), symbolic computations
also confirm that \((\partial g/\partial r)(\theta,r,0) \equiv 0\).
The function \(b(\theta,r_0) = (\partial g/\partial I)(\theta,r_0,0)\) is given
in the statement of Theorem \ref{thm:acrobot-energy-stabilization}, and by
assumption we have \(S(r_0) \geq \epsilon\) on
\(]\sqrt{60m^2gl^3},\rho[\).

All requirements of Lemma \ref{lemma:energy-regulation-D} are satisfied,
so there exists a control parameter \(I_2(\rho) > 0\) whereby the acrobot
gains energy on both \(\mathcal{R}^+\) and \(\mathcal{R}^-\) for
each \(I \in \, ]0,I_2(\rho)]\).
Let \(I_1^\star\) be the value we found for \(\mathcal{O}_1\) in 
Section \ref{sec:proof-o1}.
Taking \(I^{\star\star} = \min \{I_1^\star, I_2(\rho)\}\),
the acrobot gains/loses energy on \(\mathcal{O}_2(\rho)\)
for each \(I \in \,]0, I^{\star\star}]\).
If instead \(I \in [-I^{\star\star},0[\), the acrobot dissipates energy on
\(\mathcal{O}_2(\rho)\).
This completes the proof of Theorem \ref{thm:acrobot-energy-stabilization}.
